
\vspace{-20pt}
\section*{Work Experience}
\vspace{-20pt}
% ── Job 1 ──────────────────────────────────────────────────────────────────
\noindent
\begin{tabularx}{\linewidth}{@{}X r@{}}
  \textbf{Mondee, Fairmont, CA, USA} & \textbf{01/2023 -- current}\\
  \textit{Role: Data Scientist} &
\end{tabularx}

\textbf{Responsibilities:}
\begin{itemize}
  \item Developed GenAI-powered solutions to automate internal customer support processes using
        Snowflake Cortex AI, LangChain, and Snowflake's native vector search capabilities. These
        solutions enhanced response accuracy and significantly reduced the manual workload.

  \item Fine-tuned and deployed advanced transformer models like GPT and BERT using Snowflake ML
        and Snowpark Python. Applied these models for product feedback summarization, marketing
        content creation, and intelligent automation workflows.

  \item Implemented sophisticated RAG (Retrieval-Augmented Generation) pipelines within Snowflake
        using Cortex Search to enable context-aware responses from company data. Used Snowflake
        Model Explainability and visual explainers to interpret model outputs and demonstrate
        measurable business impact.

  \item Designed and deployed generative models such as Stable Diffusion and GANs within
        Snowflake-integrated compute environments to create synthetic images for packaging mockups
        and marketing creatives. These models also supported the generation of augmented training
        datasets.

  \item Built scalable computer vision solutions using Snowpark Container Services to perform image
        tagging, content moderation, OCR text extraction, and quality control checks on product
        packaging lines.

  \item Designed and tested intelligent chatbots using Snowflake Cortex AI and Snowpark-hosted
        inference endpoints for debugging and iteration. These chatbots handled internal employee
        queries and enhanced customer interactions across various platforms.

  \item Led prompt engineering initiatives on Snowflake Cortex LLM Functions to augment data
        synthesis, image and video generation, and AI-assisted content creation. Created frameworks
        to standardize prompt design and improve output quality consistently across teams.

  \item Developed, trained, and optimized Machine Learning and Deep Learning models for AI
        initiatives including Generative AI, NLP, and Computer Vision use cases using Snowflake ML;
        owned the end-to-end model development lifecycle from experimentation through production
        deployment via Snowflake MLOps tooling.

  \item Translated complex data science methodologies and data insights into actionable strategies
        by collaborating cross-functionally with stakeholders and business owners; ensured alignment
        to business acumen, decision-making goals, and real-world constraints.

  \item Created clear presentations, dashboards, and data visualization deliverables to communicate
        technical models and AI/ML methodologies to non-technical audiences; improved stakeholder
        understanding and adoption of deployed AI solutions.

  \item Engineered and optimized end-to-end machine learning pipelines across regression,
        time-series forecasting, and deep learning (CNN, RNN, LSTM) models; advanced Generative AI
        solutions by integrating LLMs and foundation models using LoRA and PEFT techniques for
        optimal performance, efficiency, and safety.

  \item Orchestrated end-to-end MLOps workflows on Databricks, automating model deployment and
        lifecycle management with Docker, FastAPI, and serverless functions; developed scalable,
        secure AI endpoints and intuitive front-end interfaces using Streamlit and modern web
        technologies (HTML, CSS, JavaScript).

  \item Designed robust system architectures ensuring data quality, infrastructure reliability, and
        seamless integration across pipelines; served as a technical SME guiding junior engineers
        and cross-functional teams to enhance AI governance, scalability, and enterprise adoption.

  \item Demonstrated expertise in Python and its data ecosystem (pandas, polars, NumPy, scikit-learn,
        PyTorch) with advanced capabilities in data cleaning, feature engineering, visualization
        (Seaborn), and end-to-end ML lifecycle automation using Databricks AutoML and model
        orchestration.

  \item Experienced in Generative AI and cloud-native development, including LLM fine-tuning,
        prompt optimization, latency evaluation, and deployment on AWS/Azure using Docker, Git,
        VSCode, and CI/CD workflows to deliver scalable, production-ready AI solutions.

  \item Built AI/ML pipelines in the public cloud (AWS, Azure, GCP) to deliver Performance
        Analytics, using secure data storage patterns (IAM/RBAC, encryption, least-privilege
        access) and Apache-based components where needed.

  \item Led design, development, and deployment of AI-driven product solutions by building scalable
        Python backend services and microservices using FastAPI\slash Flask, exposing secure RESTful and
        event-driven APIs with asynchronous programming, threading, and performance optimization in
        partnership with product, architecture, management, and end customers.

  \item Built and integrated AI/ML and LLM-driven solutions (Generative AI, prompt engineering,
        AI service orchestration) including model inference services, data pipelines, and API
        exposure; applied Supervised Learning, Data Science, and Data Engineering practices using
        PyTorch/TensorFlow/Scikit-learn with model lifecycle management, monitoring, and inference
        performance tuning.

  \item Developed and maintained modern UI applications in Angular with TypeScript, RxJS,
        component-based architecture, and state management; integrated UI with secure Python backend
        APIs while ensuring responsive UI design, accessibility standards, and UI performance
        optimization.

  \item Processed large-scale datasets using big data frameworks such as Hadoop and Spark to support
        data-driven AI workflows. Visualized insights with Tableau and built custom web tools with
        Flask to deliver business intelligence to stakeholders.
\end{itemize}

\textbf{Environment:} LLM-powered solutions, UX designers, CI/CD solutions, FastAPI, Docker, LLM APIs,
OpenAI API, RAG, LangChain, vector databases, Azure, Bot Framework, Chat Bot, R Studio, AWS S3, NLP,
EC2, Neural networks, SVM, Decision trees, ML, ad-hoc, MAHOUT, NOSQL, MDM, MLib \& PyAWS, anomaly
detection, develop predictive models, Performance Analytics, machine learning, data storage, public
cloud, forecasting, snowflake, Scripting, security, apache, azure, AI/ML, ETL, GCP.
