% ── Job 2 ──────────────────────────────────────────────────────────────────
\noindent
\begin{tabularx}{\linewidth}{@{}X r@{}}
  \textbf{Cosmic Reality, Hyderabad, India} & \textbf{04/2020 -- 10/2022}\\
  \textit{Role: Data Scientist} &
\end{tabularx}

\textbf{Responsibilities:}
\begin{itemize}
  \item Built an NL-to-SQL ``Data Copilot'' that converts natural-language questions into validated
        SQL and returns grounded results from enterprise datasets hosted on Snowflake.

  \item Converted regulatory documents from PDFs to structured XML and CSV formats using Python,
        automating two-way transformations from raw XML to processed formats. Used PDFMiner,
        PyPDF2, PDFQuery, and Uni-decode.

  \item Utilized Element Tree (ET) in Python to parse XML files derived from PDF conversions,
        isolating tags and attributes to map content like headings and subheadings. Structured this
        data into clean CSV rows for downstream analysis.

  \item Applied Text Mining and NLP techniques to extract opinions and sentiments from technical
        documentation and customer feedback. Leveraged NLTK, Scikit-learn, and Python libraries
        to detect trends and quality concerns.

  \item Created a spam detection pipeline and sentiment analysis model using Scikit-learn, NLTK,
        and SciPy. These models processed product reviews and internal reports, enhancing insights
        into customer satisfaction.

  \item Created predictive models to analyse user behaviour, social network structures, and web
        interactions using Pandas, NumPy, and Scikit-learn. Employed feature engineering and model
        tuning to address manufacturing quality issues.

  \item Deployed and managed containerized applications on Snowflake using Kubernetes, ensuring
        performance, scalability, and reliability across cloud-hosted workloads.

  \item Built and iteratively improved AI/ML and deep learning models across Generative AI, NLP,
        and CV initiatives, taking ownership of the full lifecycle from model design and training
        through evaluation and production deployment (MLOps).

  \item Implemented LLM-powered solutions using fine-tuning, multi-agent systems, and inference
        optimization to enhance response quality and reduce latency/cost, operationalizing advanced
        AI models to deliver business value.

  \item Converted complex data science methodologies into actionable business insights by partnering
        with stakeholders and business owners, aligning AI/ML work to business acumen, strategy,
        and decision-making.

  \item Delivered executive-ready presentations, dashboards, and data visualizations to clearly
        explain technical models and AI methodologies to non-technical audiences, accelerating
        adoption of deployed ML solutions.

  \item Developed and optimized full-cycle machine learning pipelines spanning regression,
        time-series forecasting, and deep learning (CNN, RNN, LSTM); advanced Generative AI
        initiatives by deploying LLMs and foundation models through LoRA and PEFT for maximized
        performance, efficiency, and safety.

  \item Implemented comprehensive MLOps frameworks within Databricks, streamlining model deployment
        and lifecycle automation via Docker, FastAPI, and serverless architectures; built secure,
        scalable AI endpoints and dynamic front-end interfaces using Streamlit and modern web
        stacks (HTML, CSS, JavaScript).

  \item Architected resilient system designs ensuring strong data integrity, infrastructure
        stability, and seamless integration across workflows; acted as a technical subject matter
        expert mentoring junior engineers and driving AI governance, scalability, and
        enterprise-wide adoption.

  \item Exhibited advanced proficiency in Python and its analytics stack (pandas, polars, NumPy,
        scikit-learn, PyTorch) with deep expertise in feature engineering, data optimization, and
        visual analytics (Seaborn); automated ML lifecycles using Databricks AutoML and orchestrated
        best practices.

  \item Specialized in Generative AI and cloud-native engineering, executing LLM fine-tuning, prompt
        refinement, performance benchmarking, and deployment across AWS/Azure using Docker, Git,
        VSCode, and CI/CD for reliable, production-grade AI delivery.

  \item Collaborated cross-functionally with product development, QA, platform, architecture, and
        security teams to deliver enterprise applications by designing and maintaining scalable Python
        backend services and microservices (Django\slash FastAPI\slash Flask), building secure RESTful and
        event-driven APIs with async programming, threading, reliability, scalability, and
        performance optimization.

  \item Implemented AI/ML and LLM solutions across Deep Learning and Machine Learning, including
        Generative AI, prompt engineering, inference services, and data pipelines; operationalized
        supervised learning workflows with PyTorch/TensorFlow/Scikit-learn, plus model monitoring,
        lifecycle management, and inference performance tuning for production-grade deployments.

  \item Delivered Angular UI applications using TypeScript, RxJS, state management, and
        component-based architecture; ensured seamless integration with Python backends and secure
        API consumption, while applying responsive UI design, accessibility standards, and
        front-end performance optimization.

  \item Handled containerization and platform engineering using Docker and Kubernetes on Bare Metal
        (KOB) with CI/CD and infrastructure automation; handled cluster upgrades/troubleshooting and
        platform configurations (CNI, CSI, ingress), implemented monitoring and observability, and
        applied security-by-design end-to-end to achieve high availability and fault tolerance,
        supported by unit/integration testing, code reviews.

  \item Used R for advanced statistical visualization and correlation analysis. Combined Seaborn,
        Matplotlib, and Python to present findings through interactive dashboards for engineering
        and management teams.
\end{itemize}

\textbf{Environment:} Python 2.x, CDHS, HDFS, C\#, Hadoop 2.3, Hive, Impala, AWS, Linux, Spark,
Tableau Desktop, SQL Server 2012, Databricks, Spark SQL, PySpark, Scikit-learn, XGBoost, Pandas,
NumPy, SQL, AUC-ROC, F1-score, confusion matrix, NLTK, spaCy, TextBlob, Apache Spark, Airflow,
K-Means, DBSCAN, Seaborn, ARIMA, MLflow, GitHub Actions, Jupyter, PostgreSQL, Git,AWS, anomaly
detection, develop predictive models, Performance Analytics, machine learning, data storage, public
cloud, forecasting, snowflake, Scripting, security, apache, azure, AI/ML, ETL, GCP.
