% ════════════════════════════════════════════════════════════════════════════
%  PROFILE SUMMARY
% ════════════════════════════════════════════════════════════════════════════
\vspace{-30pt}
\section*{Profile Summary}
\vspace{-20pt}
\begin{itemize}
  \item Extensive professional expertise spanning various IT domains; dedicated machine learning
        professional and data-driven analyst. Worked closely with architects, data governance teams,
        platform engineers, networking and security teams to implement end-to-end applications and
        model lifecycles, ensuring smooth development and deployment of AI models based on
        architecture designs.

  \item Designed and scaled multi-agent AI systems capable of supporting large, globally distributed
        user bases across finance and retail domains. Led the architectural design of agentic AI
        platforms, focusing on composability, coordination, and scalability of multiple autonomous
        agents.

  \item Built and validated multi-agent architectural patterns through hands-on coding to demonstrate
        correctness and feasibility to engineering teams. Architected AI-native platforms on Snowflake
        integrating Cortex AI and Snowpark models with scalable application and data layers.

  \item Evaluated and evolved agentic architectures to ensure scalability, maintainability, and
        production-readiness at high traffic volumes. Led architectural decisions around model
        selection, prompt strategies, and evaluation workflows within Snowflake Cortex environments.

  \item Used AI tools extensively in daily development and design workflows to accelerate architecture
        exploration and decision-making. Established technical standards for multi-agent AI systems,
        raising the architectural bar across distributed engineering teams.

  \item Deployed and managed AI workloads on Snowflake using container services and Snowpark Container
        Runtime, ensuring reliability, scalability, and controlled rollout strategies. Deployed and
        managed multiple generative AI models in Snowflake, aligning performance, cost, and security
        needs.

  \item Designed secure and compliant AI architectures on Snowflake leveraging role-based access
        control, fine-grained object privileges, and policy enforcement. Integrated Snowflake Cortex
        with downstream services such as APIs, data platforms, and monitoring stacks to support
        real-world workloads.

  \item Hands-on with advanced techniques like Prompt Engineering, Fine-tuning, Transfer Learning,
        RAG (Retrieval-Augmented Generation), few-shot and zero-shot learning. Applies these to
        improve accuracy, adaptability.

  \item Built generative AI applications for text generation, image synthesis, code generation,
        conversational agents, and synthetic data creation. Ensures output relevance through feedback
        loops and model evaluation metrics.

  \item Develops deep learning solutions using PyTorch, TensorFlow, Keras, and JAX. Implements and
        customizes neural networks for domain-specific use cases with optimized training strategies.

  \item Experienced in natural language processing with Hugging Face Transformers, spaCy, LangChain,
        and NLTK. Builds NLP pipelines for sentiment analysis, summarization, entity extraction, and
        conversational interfaces.

  \item Skilled in computer vision and multimodal systems using OpenCV, CLIP, DALL-E, and Stable
        Diffusion. Integrates image, text, and audio data for richer, context-aware AI models.

  \item Tracks and manages experiments using Weights \& Biases, MLflow, and TensorBoard. Facilitates
        reproducibility, version control, and model performance comparison in collaborative
        environments.

  \item Designs semantic search and vector-based retrieval systems using FAISS, Pinecone, Weaviate,
        and Chroma DB. Supports RAG pipelines and hybrid search strategies for scalable inference.

  \item Processes large datasets efficiently with Pandas, NumPy, Dask, and PySpark. Builds modular
        data pipelines for feature engineering, transformation, and analytics at scale. Automates
        workflows and data pipelines using Airflow and Prefect. Schedules training, evaluation, and
        retraining jobs to ensure reliable, continuous delivery in ML systems.

  \item Works across cloud platforms such as AWS (SageMaker, EC2, Lambda), GCP (Vertex AI), and
        Azure. Builds and manages infrastructure for training, serving, and monitoring AI models.

  \item Implements DevOps and MLOps practices using Docker, Kubernetes, GitHub Actions, and Jenkins.
        Creates CI/CD pipelines to automate model deployment, testing, and rollback strategies.

  \item Integrates AI services using OpenAI, Cohere, Anthropic Claude, Amazon Bedrock, and Hugging
        Face Hub. Develops REST and gRPC APIs with FastAPI, Flask, and gRPC for seamless system
        communication.
\end{itemize}
