%% Bhanu Prakash Bathini — Professional Resume
%% Compiler: XeLaTeX or pdfLaTeX
%% Required packages: geometry, titlesec, enumitem, hyperref, fontawesome5, multicol, xcolor, parskip

\documentclass[11pt,letterpaper]{article}

% ─── PACKAGES ────────────────────────────────────────────────────────────────
\usepackage[
  top=0.35in, bottom=0.35in,
  left=0.45in, right=0.45in
]{geometry}
\usepackage[explicit]{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{array}
\usepackage{tabularx}
\usepackage{parskip}
\usepackage{microtype}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

% ─── COLORS ──────────────────────────────────────────────────────────────────
\definecolor{HEADINGBLUE}{RGB}{0, 0, 0} 
\definecolor{RULECOLOR}{RGB}{0, 0, 0} 
\definecolor{DARKGRAY}{RGB}{0, 0, 0}
\definecolor{LINKBLUE}{RGB}{0, 0, 0}  

% ─── HYPERREF ────────────────────────────────────────────────────────────────
\hypersetup{
  colorlinks=true,
  urlcolor=black,
  linkcolor=black
}

% ─── FONTS ───────────────────────────────────────────────────────────────────
\renewcommand{\familydefault}{\sfdefault}

% ─── NO PAGE NUMBER ──────────────────────────────────────────────────────────
\pagestyle{empty}

% ─── SECTION FORMATTING ──────────────────────────────────────────────────────
\titleformat{\section}[block]
  {\color{HEADINGBLUE}\large\bfseries} % formatting
  {}{0pt}%
  {\titleline{\hrulefill\ \MakeUppercase{#1}\ \hrulefill}}

\titlespacing*{\section}{0pt}{2pt}{1pt}

% ─── LIST SETTINGS ───────────────────────────────────────────────────────────
\setlist[itemize]{
  leftmargin=1.2em,
  itemsep=0pt,
  topsep=1pt,
  parsep=0pt,
  partopsep=0pt,
  label=\textbullet
}

% ─── CUSTOM COMMANDS ─────────────────────────────────────────────────────────
\newcommand{\resumeheading}[4]{%
  \noindent
  \begin{tabularx}{\linewidth}{@{}X r@{}}
    \textbf{#1}, \textit{#2} & \textbf{#3}\\[-2pt]
    \textit{Role: #4} &
  \end{tabularx}\vspace{2pt}%
}

\newcommand{\skillrow}[2]{%
  \noindent\textbf{#1:} #2\par\vspace{1pt}%
}

% ─── DOCUMENT ────────────────────────────────────────────────────────────────
\begin{document}

% ════════════════════════════════════════════════════════════════════════════
%  HEADER
% ════════════════════════════════════════════════════════════════════════════
\begin{center}
  {\Huge\bfseries\color{HEADINGBLUE} BHANU PRAKASH BATHINI}\\[1pt]
  {\normalsize Houston, TX \quad|\quad
   \href{https://www.linkedin.com/}{LinkedIn} \quad|\quad
   \href{https://github.com/}{GitHub Profile} \quad|\quad
   \href{https://portfolio.dev/}{Portfolio}}
\end{center}

% ════════════════════════════════════════════════════════════════════════════
%  OBJECTIVE
% ════════════════════════════════════════════════════════════════════════════
\vspace{-8pt}
\section*{Objective}
\vspace{-6pt}

\noindent\textbf{Senior Data Scientist} with expertise in AI/ML, LLMs, NLP, Computer Vision, and Generative AI. Proven track record in designing and deploying scalable, advanced AI models across healthcare, finance, and e-commerce using Python, PyTorch, and Hugging Face.

% ════════════════════════════════════════════════════════════════════════════
%  PROFILE SUMMARY
% ════════════════════════════════════════════════════════════════════════════
\vspace{-8pt}
\section*{Profile Summary}
\vspace{-6pt}
\begin{itemize}
  \item Designed and scaled multi-agent AI systems and generative AI applications, supporting globally distributed users across finance and retail domains.
  \item Architected AI-native platforms on Snowflake Cortex AI and Snowpark, integrating advanced techniques like RAG, fine-tuning, and prompt engineering.
  \item Built deep learning solutions and NLP pipelines using PyTorch, TensorFlow, Hugging Face, and LangChain for domain-specific use cases.
  \item Orchestrated end-to-end MLOps workflows using Docker, Kubernetes, GitHub Actions, and Airflow for continuous model deployment.
\end{itemize}

% ════════════════════════════════════════════════════════════════════════════
%  TECHNICAL SKILLS
% ════════════════════════════════════════════════════════════════════════════
\vspace{-8pt}
\section*{Technical Skills}
\vspace{-6pt}

\begin{itemize}
  \item \textbf{Generative AI \& Deep Learning:} Transformers (GPT, BERT, LLaMA), Diffusion Models, RAG, Fine-tuning, PyTorch, TensorFlow, Keras, JAX
  \item \textbf{NLP \& CV:} Hugging Face, LangChain, spaCy, NLTK, OpenCV, CLIP, Stable Diffusion
  \item \textbf{Data \& Vector DBs:} Pandas, NumPy, PySpark, FAISS, Pinecone, Weaviate, Chroma DB
  \item \textbf{Cloud \& MLOps:} AWS, GCP, Azure, Docker, Kubernetes, CI/CD, Airflow, MLflow
  \item \textbf{Languages \& Others:} Python, SQL, JavaScript (Node.js), C++, TypeScript, Bash
\end{itemize}

% ════════════════════════════════════════════════════════════════════════════
%  WORK EXPERIENCE
% ════════════════════════════════════════════════════════════════════════════
\vspace{-8pt}
\section*{Work Experience}
\vspace{-6pt}

% ── Job 1 ──────────────────────────────────────────────────────────────────
\noindent
\begin{tabularx}{\linewidth}{@{}X r@{}}
  \textbf{Mondee, Fairmont, CA, USA} & \textbf{01/2023 -- current}\\
  \textit{Role: Data Scientist} &
\end{tabularx}

\textbf{Responsibilities:}
\begin{itemize}
  \item Developed GenAI-powered solutions using Snowflake Cortex AI, LangChain, and vector search to automate customer support processes.
  \item Implemented sophisticated RAG pipelines within Snowflake to enable context-aware responses from enterprise data.
  \item Fine-tuned and deployed transformer models (GPT, BERT) for product feedback summarization and intelligent automation workflows.
  \item Orchestrated end-to-end MLOps workflows on Databricks, automating deployment via Docker, FastAPI, and serverless functions.
\end{itemize}

\textbf{Environment:} LLM APIs, OpenAI, RAG, LangChain, Snowflake, Databricks, FastAPI, Docker, Azure, AWS, Python, Vector databases.

\vspace{0pt}

% ── Job 2 ──────────────────────────────────────────────────────────────────
\noindent
\begin{tabularx}{\linewidth}{@{}X r@{}}
  \textbf{Cosmic Reality, Hyderabad, India} & \textbf{04/2020 -- 10/2022}\\
  \textit{Role: Data Scientist} &
\end{tabularx}

\textbf{Responsibilities:}
\begin{itemize}
  \item Built an NL-to-SQL ``Data Copilot'' converting natural-language into validated SQL for enterprise datasets hosted on Snowflake.
  \item Created predictive models and applied Text Mining and NLP techniques to extract sentiments from technical documentation.
  \item Deployed and managed containerized AI applications using Kubernetes, ensuring high performance across cloud-hosted workloads.
  \item Streamlined model deployment and lifecycle automation using Databricks, Docker, FastAPI, and Streamlit.
\end{itemize}

\textbf{Environment:} Python, Hadoop, Spark, Snowflake, Databricks, AWS, GCP, Scikit-learn, MLflow, Kubernetes, Pandas, SQL.

% ════════════════════════════════════════════════════════════════════════════
%  EDUCATION
% ════════════════════════════════════════════════════════════════════════════
\vspace{-8pt}
\section*{Education}
\vspace{-6pt}
\noindent Master's in Applied Computer Science, \textbf{Northwest Missouri State University},
Maryville, Missouri, USA \hfill \textbf{06/2023 -- 12/2024}
\end{document}
