%% Bhanu Prakash Bathini — Professional Resume
%% Compiler: XeLaTeX or pdfLaTeX
%% Required packages: geometry, titlesec, enumitem, hyperref, fontawesome5, multicol, xcolor, parskip

\documentclass[11pt,letterpaper]{article}

% ─── PACKAGES ────────────────────────────────────────────────────────────────
\usepackage[
  top=0.45in, bottom=0.45in,
  left=0.55in, right=0.55in
]{geometry}
\usepackage[explicit]{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{array}
\usepackage{tabularx}
\usepackage{parskip}
\usepackage{microtype}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}


% ─── COLORS ──────────────────────────────────────────────────────────────────
\definecolor{HEADINGBLUE}{RGB}{0, 0, 0} 
\definecolor{RULECOLOR}{RGB}{0, 0, 0} 
\definecolor{DARKGRAY}{RGB}{0, 0, 0}
\definecolor{LINKBLUE}{RGB}{0, 0, 0}  

% ─── HYPERREF ────────────────────────────────────────────────────────────────
\hypersetup{
  colorlinks=true,
  urlcolor=black,
  linkcolor=black
}

% ─── FONTS ───────────────────────────────────────────────────────────────────
\renewcommand{\familydefault}{\sfdefault}

% ─── NO PAGE NUMBER ──────────────────────────────────────────────────────────
\pagestyle{empty}

% ─── SECTION FORMATTING ──────────────────────────────────────────────────────
\titleformat{\section}[block]
  {\color{HEADINGBLUE}\large\bfseries} % formatting
  {}{0pt}%
  {\titleline{\hrulefill\ \MakeUppercase{#1}\ \hrulefill}}

\titlespacing*{\section}{0pt}{8pt}{4pt}

% ─── LIST SETTINGS ───────────────────────────────────────────────────────────
\setlist[itemize]{
  leftmargin=1.2em,
  itemsep=1pt,
  topsep=2pt,
  parsep=0pt,
  partopsep=0pt,
  label=\textbullet
}

% ─── CUSTOM COMMANDS ─────────────────────────────────────────────────────────
\newcommand{\resumeheading}[4]{%
  \noindent
  \begin{tabularx}{\linewidth}{@{}X r@{}}
    \textbf{#1}, \textit{#2} & \textbf{#3}\\[-2pt]
    \textit{Role: #4} &
  \end{tabularx}\vspace{2pt}%
}

\newcommand{\skillrow}[2]{%
  \noindent\textbf{#1:} #2\par\vspace{1pt}%
}

% ─── DOCUMENT ────────────────────────────────────────────────────────────────
\begin{document}

% ════════════════════════════════════════════════════════════════════════════
%  HEADER
% ════════════════════════════════════════════════════════════════════════════
\begin{center}

  {\Huge\bfseries\color{HEADINGBLUE} BHANU PRAKASH BATHINI}\\[4pt]
  {\normalsize Houston, TX \quad|\quad
   \href{https://www.linkedin.com/}{LinkedIn} \quad|\quad
   \href{https://github.com/}{GitHub Profile} \quad|\quad
   \href{https://portfolio.dev/}{Portfolio}}
\end{center}


% ════════════════════════════════════════════════════════════════════════════
%  OBJECTIVE
% ════════════════════════════════════════════════════════════════════════════
\vspace{-20pt}
\section*{Objective}
\vspace{-20pt}

\noindent\textbf{Senior Data Scientist} with Hands-on applied AI/ML, LLMs, NLP, Computer Vision,
Generative AI and designing and deploying advanced AI models, including LLMs and diffusion models
for NLP, vision, and multimodal applications. Proficient in Python, PyTorch, TensorFlow, and Hugging
Face with expertise in model fine-tuning, prompt engineering, and MLOps. Proven track record in
building scalable AI solutions across healthcare, finance, and e-commerce domains.
% ════════════════════════════════════════════════════════════════════════════
%  PROFILE SUMMARY
% ════════════════════════════════════════════════════════════════════════════
\vspace{-30pt}
\section*{Profile Summary}
\vspace{-20pt}
\begin{itemize}
  \item Extensive professional expertise spanning various IT domains; dedicated machine learning
        professional and data-driven analyst. Worked closely with architects, data governance teams,
        platform engineers, networking and security teams to implement end-to-end applications and
        model lifecycles, ensuring smooth development and deployment of AI models based on
        architecture designs.

  \item Designed and scaled multi-agent AI systems capable of supporting large, globally distributed
        user bases across finance and retail domains. Led the architectural design of agentic AI
        platforms, focusing on composability, coordination, and scalability of multiple autonomous
        agents.

  \item Built and validated multi-agent architectural patterns through hands-on coding to demonstrate
        correctness and feasibility to engineering teams. Architected AI-native platforms on Snowflake
        integrating Cortex AI and Snowpark models with scalable application and data layers.

  \item Evaluated and evolved agentic architectures to ensure scalability, maintainability, and
        production-readiness at high traffic volumes. Led architectural decisions around model
        selection, prompt strategies, and evaluation workflows within Snowflake Cortex environments.

  \item Used AI tools extensively in daily development and design workflows to accelerate architecture
        exploration and decision-making. Established technical standards for multi-agent AI systems,
        raising the architectural bar across distributed engineering teams.

  \item Deployed and managed AI workloads on Snowflake using container services and Snowpark Container
        Runtime, ensuring reliability, scalability, and controlled rollout strategies. Deployed and
        managed multiple generative AI models in Snowflake, aligning performance, cost, and security
        needs.

  \item Designed secure and compliant AI architectures on Snowflake leveraging role-based access
        control, fine-grained object privileges, and policy enforcement. Integrated Snowflake Cortex
        with downstream services such as APIs, data platforms, and monitoring stacks to support
        real-world workloads.

  \item Hands-on with advanced techniques like Prompt Engineering, Fine-tuning, Transfer Learning,
        RAG (Retrieval-Augmented Generation), few-shot and zero-shot learning. Applies these to
        improve accuracy, adaptability.

  \item Built generative AI applications for text generation, image synthesis, code generation,
        conversational agents, and synthetic data creation. Ensures output relevance through feedback
        loops and model evaluation metrics.

  \item Develops deep learning solutions using PyTorch, TensorFlow, Keras, and JAX. Implements and
        customizes neural networks for domain-specific use cases with optimized training strategies.

  \item Experienced in natural language processing with Hugging Face Transformers, spaCy, LangChain,
        and NLTK. Builds NLP pipelines for sentiment analysis, summarization, entity extraction, and
        conversational interfaces.

  \item Skilled in computer vision and multimodal systems using OpenCV, CLIP, DALL-E, and Stable
        Diffusion. Integrates image, text, and audio data for richer, context-aware AI models.

  \item Tracks and manages experiments using Weights \& Biases, MLflow, and TensorBoard. Facilitates
        reproducibility, version control, and model performance comparison in collaborative
        environments.

  \item Designs semantic search and vector-based retrieval systems using FAISS, Pinecone, Weaviate,
        and Chroma DB. Supports RAG pipelines and hybrid search strategies for scalable inference.

  \item Processes large datasets efficiently with Pandas, NumPy, Dask, and PySpark. Builds modular
        data pipelines for feature engineering, transformation, and analytics at scale. Automates
        workflows and data pipelines using Airflow and Prefect. Schedules training, evaluation, and
        retraining jobs to ensure reliable, continuous delivery in ML systems.

  \item Works across cloud platforms such as AWS (SageMaker, EC2, Lambda), GCP (Vertex AI), and
        Azure. Builds and manages infrastructure for training, serving, and monitoring AI models.

  \item Implements DevOps and MLOps practices using Docker, Kubernetes, GitHub Actions, and Jenkins.
        Creates CI/CD pipelines to automate model deployment, testing, and rollback strategies.

  \item Integrates AI services using OpenAI, Cohere, Anthropic Claude, Amazon Bedrock, and Hugging
        Face Hub. Develops REST and gRPC APIs with FastAPI, Flask, and gRPC for seamless system
        communication.
\end{itemize}

% ════════════════════════════════════════════════════════════════════════════
%  TECHNICAL SKILLS
% ════════════════════════════════════════════════════════════════════════════
\vspace{-20pt}
\section*{Technical Skills}
\vspace{-20pt}

\noindent\textbf{Generative AI \& Deep Learning:}

\begin{itemize}
  \item \textbf{Models:} Transformers (GPT, BERT, T5, LLaMA), GANs, VAEs, Diffusion Models, Auto encoders
  \item \textbf{Techniques:} Prompt Engineering, Fine-tuning, Transfer Learning, RAG (Retrieval-Augmented Generation), Few-shot \& Zero-shot Learning
  \item \textbf{Applications:} Text Generation, Image Synthesis, Conversational AI, Code Generation, Synthetic Data
  \item \textbf{Deep Learning:} PyTorch, Tensor Flow, Keras, JAX
  \item \textbf{NLP:} Hugging Face Transformers, spaCy, NLTK, Lang Chain
  \item \textbf{CV \& Multimodal:} OpenCV, DALL-E, CLIP, Stable Diffusion
  \item \textbf{Experiment Tracking:} Weights \& Biases, Tensor Board, MLflow
  \item \textbf{Vector Databases:} FAISS, Pinecone, Weaviate, Chroma DB
  \item \textbf{Data Processing:} Pandas, NumPy, Dask, PySpark
  \item \textbf{Workflow Orchestration:} Airflow, Prefect
  \item \textbf{Model Deployment:} ONNX, Torch Serve, Tensor Flow Serving
  \item \textbf{Cloud Platforms:} AWS (SageMaker, EC2, Lambda), GCP (Vertex AI), Azure
  \item \textbf{DevOps Tools:} Docker, Kubernetes, GitHub Actions, Jenkins
  \item \textbf{MLOps:} CI/CD Pipelines, Model Monitoring, Version Control
  \item \textbf{Core Languages:} Python, JavaScript (Node.js), Bash
  \item \textbf{Others:} SQL, C++, TypeScript (for frontend integration of AI tools), AWS, anomaly detection,
        Artificial Intelligence (AI), Machine Learning (ML), Deep Learning and Generative AI, with hands-on
        experience building Large Language Model (LLM) solutions for Natural Language Processing (NLP) and
        Computer Vision (CV) use cases, including multi-agent systems, fine-tuning, training, evaluating, and
        deploying production ML models end-to-end; translating complex data science methodologies into
        actionable business insights; partnering cross-functionally with stakeholders and business owners;
        communicating results to non-technical audiences through clear presentations, dashboards, and data
        visualization to drive measurable business value.
\end{itemize}

% ════════════════════════════════════════════════════════════════════════════
%  WORK EXPERIENCE
% ════════════════════════════════════════════════════════════════════════════
\vspace{-20pt}
\section*{Work Experience}
\vspace{-20pt}

% ── Job 1 ──────────────────────────────────────────────────────────────────
\noindent
\begin{tabularx}{\linewidth}{@{}X r@{}}
  \textbf{Mondee, Fairmont, CA, USA} & \textbf{01/2023 -- current}\\
  \textit{Role: Data Scientist} &
\end{tabularx}

\textbf{Responsibilities:}
\begin{itemize}
  \item Developed GenAI-powered solutions to automate internal customer support processes using
        Snowflake Cortex AI, LangChain, and Snowflake's native vector search capabilities. These
        solutions enhanced response accuracy and significantly reduced the manual workload.

  \item Fine-tuned and deployed advanced transformer models like GPT and BERT using Snowflake ML
        and Snowpark Python. Applied these models for product feedback summarization, marketing
        content creation, and intelligent automation workflows.

  \item Implemented sophisticated RAG (Retrieval-Augmented Generation) pipelines within Snowflake
        using Cortex Search to enable context-aware responses from company data. Used Snowflake
        Model Explainability and visual explainers to interpret model outputs and demonstrate
        measurable business impact.

  \item Designed and deployed generative models such as Stable Diffusion and GANs within
        Snowflake-integrated compute environments to create synthetic images for packaging mockups
        and marketing creatives. These models also supported the generation of augmented training
        datasets.

  \item Built scalable computer vision solutions using Snowpark Container Services to perform image
        tagging, content moderation, OCR text extraction, and quality control checks on product
        packaging lines.

  \item Designed and tested intelligent chatbots using Snowflake Cortex AI and Snowpark-hosted
        inference endpoints for debugging and iteration. These chatbots handled internal employee
        queries and enhanced customer interactions across various platforms.

  \item Led prompt engineering initiatives on Snowflake Cortex LLM Functions to augment data
        synthesis, image and video generation, and AI-assisted content creation. Created frameworks
        to standardize prompt design and improve output quality consistently across teams.

  \item Developed, trained, and optimized Machine Learning and Deep Learning models for AI
        initiatives including Generative AI, NLP, and Computer Vision use cases using Snowflake ML;
        owned the end-to-end model development lifecycle from experimentation through production
        deployment via Snowflake MLOps tooling.

  \item Translated complex data science methodologies and data insights into actionable strategies
        by collaborating cross-functionally with stakeholders and business owners; ensured alignment
        to business acumen, decision-making goals, and real-world constraints.

  \item Created clear presentations, dashboards, and data visualization deliverables to communicate
        technical models and AI/ML methodologies to non-technical audiences; improved stakeholder
        understanding and adoption of deployed AI solutions.

  \item Engineered and optimized end-to-end machine learning pipelines across regression,
        time-series forecasting, and deep learning (CNN, RNN, LSTM) models; advanced Generative AI
        solutions by integrating LLMs and foundation models using LoRA and PEFT techniques for
        optimal performance, efficiency, and safety.

  \item Orchestrated end-to-end MLOps workflows on Databricks, automating model deployment and
        lifecycle management with Docker, FastAPI, and serverless functions; developed scalable,
        secure AI endpoints and intuitive front-end interfaces using Streamlit and modern web
        technologies (HTML, CSS, JavaScript).

  \item Designed robust system architectures ensuring data quality, infrastructure reliability, and
        seamless integration across pipelines; served as a technical SME guiding junior engineers
        and cross-functional teams to enhance AI governance, scalability, and enterprise adoption.

  \item Demonstrated expertise in Python and its data ecosystem (pandas, polars, NumPy, scikit-learn,
        PyTorch) with advanced capabilities in data cleaning, feature engineering, visualization
        (Seaborn), and end-to-end ML lifecycle automation using Databricks AutoML and model
        orchestration.

  \item Experienced in Generative AI and cloud-native development, including LLM fine-tuning,
        prompt optimization, latency evaluation, and deployment on AWS/Azure using Docker, Git,
        VSCode, and CI/CD workflows to deliver scalable, production-ready AI solutions.

  \item Built AI/ML pipelines in the public cloud (AWS, Azure, GCP) to deliver Performance
        Analytics, using secure data storage patterns (IAM/RBAC, encryption, least-privilege
        access) and Apache-based components where needed.

  \item Led design, development, and deployment of AI-driven product solutions by building scalable
        Python backend services and microservices using FastAPI/Flask, exposing secure RESTful and
        event-driven APIs with asynchronous programming, threading, and performance optimization in
        partnership with product, architecture, management, and end customers.

  \item Built and integrated AI/ML and LLM-driven solutions (Generative AI, prompt engineering,
        AI service orchestration) including model inference services, data pipelines, and API
        exposure; applied Supervised Learning, Data Science, and Data Engineering practices using
        PyTorch/TensorFlow/Scikit-learn with model lifecycle management, monitoring, and inference
        performance tuning.

  \item Developed and maintained modern UI applications in Angular with TypeScript, RxJS,
        component-based architecture, and state management; integrated UI with secure Python backend
        APIs while ensuring responsive UI design, accessibility standards, and UI performance
        optimization.

  \item Processed large-scale datasets using big data frameworks such as Hadoop and Spark to support
        data-driven AI workflows. Visualized insights with Tableau and built custom web tools with
        Flask to deliver business intelligence to stakeholders.
\end{itemize}

\textbf{Environment:} LLM-powered solutions, UX designers, CI/CD solutions, FastAPI, Docker, LLM APIs,
OpenAI API, RAG, LangChain, vector databases, Azure, Bot Framework, Chat Bot, R Studio, AWS S3, NLP,
EC2, Neural networks, SVM, Decision trees, ML, ad-hoc, MAHOUT, NOSQL, MDM, MLib \& PyAWS, anomaly
detection, develop predictive models, Performance Analytics, machine learning, data storage, public
cloud, forecasting, snowflake, Scripting, security, apache, azure, AI/ML, ETL, GCP.

\vspace{6pt}

% ── Job 2 ──────────────────────────────────────────────────────────────────
\noindent
\begin{tabularx}{\linewidth}{@{}X r@{}}
  \textbf{Cosmic Reality, Hyderabad, India} & \textbf{04/2020 -- 10/2022}\\
  \textit{Role: Data Scientist} &
\end{tabularx}

\textbf{Responsibilities:}
\begin{itemize}
  \item Built an NL-to-SQL ``Data Copilot'' that converts natural-language questions into validated
        SQL and returns grounded results from enterprise datasets hosted on Snowflake.

  \item Converted regulatory documents from PDFs to structured XML and CSV formats using Python,
        automating two-way transformations from raw XML to processed formats. Used PDFMiner,
        PyPDF2, PDFQuery, and Uni-decode.

  \item Utilized Element Tree (ET) in Python to parse XML files derived from PDF conversions,
        isolating tags and attributes to map content like headings and subheadings. Structured this
        data into clean CSV rows for downstream analysis.

  \item Applied Text Mining and NLP techniques to extract opinions and sentiments from technical
        documentation and customer feedback. Leveraged NLTK, Scikit-learn, and Python libraries
        to detect trends and quality concerns.

  \item Created a spam detection pipeline and sentiment analysis model using Scikit-learn, NLTK,
        and SciPy. These models processed product reviews and internal reports, enhancing insights
        into customer satisfaction.

  \item Created predictive models to analyse user behaviour, social network structures, and web
        interactions using Pandas, NumPy, and Scikit-learn. Employed feature engineering and model
        tuning to address manufacturing quality issues.

  \item Deployed and managed containerized applications on Snowflake using Kubernetes, ensuring
        performance, scalability, and reliability across cloud-hosted workloads.

  \item Built and iteratively improved AI/ML and deep learning models across Generative AI, NLP,
        and CV initiatives, taking ownership of the full lifecycle from model design and training
        through evaluation and production deployment (MLOps).

  \item Implemented LLM-powered solutions using fine-tuning, multi-agent systems, and inference
        optimization to enhance response quality and reduce latency/cost, operationalizing advanced
        AI models to deliver business value.

  \item Converted complex data science methodologies into actionable business insights by partnering
        with stakeholders and business owners, aligning AI/ML work to business acumen, strategy,
        and decision-making.

  \item Delivered executive-ready presentations, dashboards, and data visualizations to clearly
        explain technical models and AI methodologies to non-technical audiences, accelerating
        adoption of deployed ML solutions.

  \item Developed and optimized full-cycle machine learning pipelines spanning regression,
        time-series forecasting, and deep learning (CNN, RNN, LSTM); advanced Generative AI
        initiatives by deploying LLMs and foundation models through LoRA and PEFT for maximized
        performance, efficiency, and safety.

  \item Implemented comprehensive MLOps frameworks within Databricks, streamlining model deployment
        and lifecycle automation via Docker, FastAPI, and serverless architectures; built secure,
        scalable AI endpoints and dynamic front-end interfaces using Streamlit and modern web
        stacks (HTML, CSS, JavaScript).

  \item Architected resilient system designs ensuring strong data integrity, infrastructure
        stability, and seamless integration across workflows; acted as a technical subject matter
        expert mentoring junior engineers and driving AI governance, scalability, and
        enterprise-wide adoption.

  \item Exhibited advanced proficiency in Python and its analytics stack (pandas, polars, NumPy,
        scikit-learn, PyTorch) with deep expertise in feature engineering, data optimization, and
        visual analytics (Seaborn); automated ML lifecycles using Databricks AutoML and orchestrated
        best practices.

  \item Specialized in Generative AI and cloud-native engineering, executing LLM fine-tuning, prompt
        refinement, performance benchmarking, and deployment across AWS/Azure using Docker, Git,
        VSCode, and CI/CD for reliable, production-grade AI delivery.

  \item Collaborated cross-functionally with product development, QA, platform, architecture, and
        security teams to deliver enterprise applications by designing and maintaining scalable Python
        backend services and microservices (Django/FastAPI/Flask), building secure RESTful and
        event-driven APIs with async programming, threading, reliability, scalability, and
        performance optimization.

  \item Implemented AI/ML and LLM solutions across Deep Learning and Machine Learning, including
        Generative AI, prompt engineering, inference services, and data pipelines; operationalized
        supervised learning workflows with PyTorch/TensorFlow/Scikit-learn, plus model monitoring,
        lifecycle management, and inference performance tuning for production-grade deployments.

  \item Delivered Angular UI applications using TypeScript, RxJS, state management, and
        component-based architecture; ensured seamless integration with Python backends and secure
        API consumption, while applying responsive UI design, accessibility standards, and
        front-end performance optimization.

  \item Handled containerization and platform engineering using Docker and Kubernetes on Bare Metal
        (KOB) with CI/CD and infrastructure automation; handled cluster upgrades/troubleshooting and
        platform configurations (CNI, CSI, ingress), implemented monitoring and observability, and
        applied security-by-design end-to-end to achieve high availability and fault tolerance,
        supported by unit/integration testing, code reviews.

  \item Used R for advanced statistical visualization and correlation analysis. Combined Seaborn,
        Matplotlib, and Python to present findings through interactive dashboards for engineering
        and management teams.
\end{itemize}

\textbf{Environment:} Python 2.x, CDHS, HDFS, C\#, Hadoop 2.3, Hive, Impala, AWS, Linux, Spark,
Tableau Desktop, SQL Server 2012, Databricks, Spark SQL, PySpark, Scikit-learn, XGBoost, Pandas,
NumPy, SQL, AUC-ROC, F1-score, confusion matrix, NLTK, spaCy, TextBlob, Apache Spark, Airflow,
K-Means, DBSCAN, Seaborn, ARIMA, MLflow, GitHub Actions, Jupyter, PostgreSQL, Git,AWS, anomaly
detection, develop predictive models, Performance Analytics, machine learning, data storage, public
cloud, forecasting, snowflake, Scripting, security, apache, azure, AI/ML, ETL, GCP.

% ════════════════════════════════════════════════════════════════════════════
%  EDUCATION
% ════════════════════════════════════════════════════════════════════════════
\vspace{-20pt}
\section*{Education}
\vspace{-20pt}
\noindent Master's in Applied Computer Science, \textbf{Northwest Missouri State University},
Maryville, Missouri, USA \hfill \textbf{06/2023 -- 12/2024}
\end{document}